---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  #fig.path = "man/figures/README-",
  out.width = "100%",
  echo = FALSE, 
  warning = FALSE
  #fig.width = 10,
  #fig.height = 4.75
)

options(knitr.kable.NA = "")

library(dplyr)
library(tidyr)
library(stringr)
library(purrr)
```

```{r scrape data}
pat <- Sys.getenv("GITHUB_PAT")
pat <- switch(!pat == "", pat)

msk_repos = 
  gh::gh("GET /users/{username}/repos", username = "MSKCC-Epi-Bio", .token = pat)

fct_repo_name = 
  function(x){
    msk_repos[[x]]$name
  }

fct_repo_lang = 
  function(x){
    msk_repos[[x]]$language
  }

fct_repo_forks = 
  function(x){
    msk_repos[[x]]$forks
  }

fct_repo_updated = 
  function(x){
    msk_repos[[x]]$pushed_at
  }

fct_repo_topics = 
  function(x){
    msk_repos[[x]]$topics
  }

fct_repo_stars = 
  function(x){
    msk_repos[[x]]$stargazers_count
  }

fct_repo_url = 
  function(x){
    msk_repos[[x]]$html_url
  }

fct_repo_about = 
  function(x){
    msk_repos[[x]]$description
  }

df_repos =   
  tibble(
    name = map(.x = c(1:length(msk_repos)), ~fct_repo_name(.x)),
    url = map(.x = c(1:length(msk_repos)), ~fct_repo_url(.x)),
    language = map(.x = c(1:length(msk_repos)), ~fct_repo_lang(.x)),
    stars = map(.x = c(1:length(msk_repos)), ~fct_repo_stars(.x)),
    updated_date = map(.x = c(1:length(msk_repos)), ~fct_repo_updated(.x)),
    about = map(.x = c(1:length(msk_repos)), ~fct_repo_about(.x)),
    topic = map(.x = c(1:length(msk_repos)), ~fct_repo_topics(.x))
  ) %>% 
  tidyr::unnest(
    cols = everything()
  ) %>% 
  mutate(
    topic = as.character(topic),
    updated_date = format(as.Date(str_sub(updated_date, 1, 10)), "%m/%d/%Y")
  ) %>% 
  group_by(name) %>% 
  mutate(topic_id = row_number()) %>% 
  pivot_wider(
    names_prefix = "topic_", names_from = topic_id, values_from = topic
  ) %>% 
  unite(topic_1:last_col(), col = "topics", sep = ", ") %>% 
  mutate(
    topics = stringr::str_remove_all(topics, ", NA")
  ) %>% 
  ungroup()

# get CRAN downloads
# devtools::install_github("metacran/cranlogs")
cran_packages = 
  df_repos %>% 
  filter(str_detect(topics, "r-package")) %>% 
  pull(name)

df_cran =
  cranlogs::cran_downloads(packages = cran_packages, from = "2012-01-01") %>% 
  group_by(package) %>% 
  summarise(n_downloads = sum(count)) %>% 
  rename(name = package)

df_repos_fin = 
  df_repos %>% 
  left_join(df_cran, by = "name")

#cranlogs::cran_downloads(packages = cran_packages, from = "2012-01-01") %>% 
#  mutate(year = as.double(stringr::str_sub(date, 1, 4))) %>% 
#  filter(package != "gnomeR") %>% 
#  group_by(year, package) %>% 
#  summarise(n_downloads = sum(count)) %>% 
#  ggplot(aes(x = year, y = n_downloads, color = package)) +
#  geom_line() +
#  scale_x_continuous(
#    breaks = c(2012:2022)
#  ) +
#  labs(
#    title = "CRAN Downloads Over the Years",
#    x = "Year",
#    y = "Downloads"
#  ) +
#  theme(
#    plot.title = element_text(hjust = 0.5)
#  )
```

# **MSKCC-Epi-Bio**

This GitHub organization hosts code, presentations and other resources created by members of Memorial Sloan Kettering's Department of Epidemiology & Biostatistics.

The repositories in this organization provide resources for implementing competing risks survival analyses ([tidycmprsk](https://github.com/MSKCC-Epi-Bio/tidycmprsk)) and analyzing genomic data ([gnomeR](https://github.com/MSKCC-Epi-Bio/gnomeR)) and patient-reported outcomes ([PROscorerTools](https://github.com/MSKCC-Epi-Bio/PROscorerTools)) in R, implementing decision curves in python ([dcurves](https://github.com/MSKCC-Epi-Bio/dcurves)), as well as a set of SAS macros for common tasks such as creating a Table 1 ([msk_SAS_macros](https://github.com/MSKCC-Epi-Bio/msk_SAS_macros)). 

---

## **R Packages**

```{r packages}
# R packages table:

df_repos_fin %>% 
  filter(language == "R") %>% 
  select(-c(language, topics)) %>% 
  distinct(name, .keep_all = T) %>% 
  mutate(
    name = str_c("[", name),
    name = str_c(name, "]"),
    url = str_c("(", url),
    url = str_c(url, ")"),
    n_downloads = ifelse(n_downloads == 0, NA, n_downloads)
    ) %>% 
  unite(name_url, name, url, sep = "") %>% 
  relocate(name_url, n_downloads) %>% 
  knitr::kable(
    align = "lcccl",
    col.names = c("Package", "CRAN Downloads (All-Time)", "GitHub Stars", "Last Updated", "About")
  )

```

---

## **Python Packages**

```{r python}
# R packages table:

df_repos_fin %>% 
  filter(language == "Jupyter Notebook") %>% 
  select(-c(topics, language, n_downloads)) %>% 
  distinct(name, .keep_all = T) %>% 
  mutate(
    name = str_c("[", name),
    name = str_c(name, "]"),
    url = str_c("(", url),
    url = str_c(url, ")")
    ) %>% 
  unite(name_url, name, url, sep = "") %>% 
  relocate(name_url, ) %>% 
  knitr::kable(
    align = "lccl",
    col.names = c("Package", "GitHub Stars", "Last Updated", "About")
  )

```

---

## **SAS Repositories**

```{r sas}
df_repos_fin %>% 
  filter(language == "SAS") %>% 
  select(-c(topics, language, n_downloads)) %>% 
  distinct(name, .keep_all = T) %>% 
  mutate(
    name = str_c("[", name),
    name = str_c(name, "]"),
    url = str_c("(", url),
    url = str_c(url, ")")
    ) %>% 
  unite(name_url, name, url, sep = "") %>% 
  relocate(name_url, stars) %>% 
  knitr::kable(
    align = "lccl",
    col.names = c("Repository", "GitHub Stars", "Last Updated", "About")
  )
```

---

## **Presentations**

```{r pressy}
df_repos_fin %>% 
  filter(language %in% c("HTML", NA)) %>% 
  select(-c(topics, language, n_downloads)) %>% 
  distinct(name, .keep_all = T) %>% 
  mutate(
    name = str_c("[", name),
    name = str_c(name, "]"),
    url = str_c("(", url),
    url = str_c(url, ")")
    ) %>% 
  unite(name_url, name, url, sep = "") %>% 
  relocate(name_url, stars) %>% 
  knitr::kable(
    align = "lccl",
    col.names = c("Repository", "GitHub Stars", "Last Updated", "About")
  )
```

---

# **Contact**

Please contact Jessica Lavery (<laveryj@mskcc.org>) and Daniel Sjoberg (<sjobergd@mskcc.org>) if you are interested in creating a repository or transferring an existing repository to the organization. 
